The Bug Catalog of the Maven Ecosystem

### 2014-01-21 docs/msr.tex
adding content in the "tools and findings" section

\section{Tools and Findings}
\label{sec:find}
Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository.

@@

Cite~\cite{RDV13}.

>>>>

\section{Tools and Findings}
\label{sec:find}

As we mentioned earlier our data was stored in a
Mongo{\sc db} database. Hence, it is easy to either create
queries to find out basic information like:
``how many bad practice bugs exist in the repository", or
create scripts that can help us capture correlations
that could provide valuable findings.
Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository.

@@

The Maven ecosystem has been previously analyzed by
Raemaekers et al.~\cite{RDV13}
to produce the {\it Maven dependency dataset}.
Apart from basic information like individual methods, classes,
packages and lines of code for every {\sc jar}, this dataset
also includes a database with all the
connections between the aforementioned elements.
